Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-07 Paper/paper.tex
"Finished" draft edits. Just a couple more sections and it's done :-D

%%%%%%%%%%%%%%%%%%%%%%
%%% Sample App 
%%%   Talk about test app
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Testing Frameworks Survey}
In the following chapter we will discuss the testing frameworks that we looked at and the application we used to evaluate them.

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, making tasks as completed, and viewing completed tasks. Here is a brief preview of the application:

@@

In addition to the simplicity and ease of understanding, this application was selected because it included Node.js as we wanted to see if the tools would be able to handle our final evaluation application.
One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB calls that were made in the sample app. As many web application feature asynchronous calls, we will be discussing how the following frameworks deal with asynchronous test support.

\subsection{The Average Web Application}
In an effort to create a good workflow and collection of tools, we have chosen to focus on web applications that uses Node.js, JavaScript, Cloud Services, and a backing Database when searching for our tools. This choice was made because of the popularity of that kind of set up, as well as the fact that our evaluation application was set up in that way.

\todo{THIS IS LAME}
Although there are multiple languages and tools available for creating a backing server, we chose Node.js because of it's wide use and because it is what we're most familiar with.

JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage} We also chose JavaScript because the rest of our application was written in JavaScript and we wanted to keep things as constant as possible.

Many web applications use Cloud Services for a number of things, most often they're used for storage of the web content that's being hosted.

Web applications tend to keep track of users which most often constitutes the use of a database behind the scenes to store users and update them as necessary.

@@

\subsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the enjoyment of watching the tests execute.

Nonetheless, we still looked at two options that we will outline briefly below for other developer's reference.

\subsubsection{PhantomJS\cite{PhantomJS}}
The reigning king of headless browsers is PhantomJS. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS\cite{ZombieJS}}
ZombieJS is often the other go-to for headless browsers. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins \cite{Jenkins}}
Jenkins is the first of the continuous integration frameworks that we tried out. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}[!ht]
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run a project in. However, once the server has the necessary applications and libraries, the builds and tests will run without issue. Jenkins can run an ``unlimited'' number of builds, tests, and processes with the only limiting factor the hardware that it is running on. It is also 100\% free and can connect with public and private repositories alike.

\subsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore \cite{Semaphore}}
Semaphore is another online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI \cite{MagnumCI}}
MagnumCI is another online CI framework, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

@@

Of particular interest is that last feature, \lstinline{watch}. We are particularly fond of grunt's \lstinline{watch} capability because it means that we have tests running near constantly that give immediate feedback to the developer when they change existing code or write new code after having written a test for it. As long as all the tests are passing, the developer has a good idea that the changes made are regression-tested as well as freshly tested and are ready for publishing or integration.

\subsection{Node Inspector\cite{NodeInspector}}
Node Inspector is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.

@@

\section{Framework Decision Matrices}
\todo{What to put in these tables for columns.}
\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Async Support & Free & Separate Server & Assertion Styles & Test Interfaces & Reporters \\ \hline
Jasmine   & X             & X    &                 &                  &                 &           \\ \hline
Mocha     & X             & X    &                 & X*               & X               & X         \\ \hline
Qunit     & X             & X    &                 &                  &                 &           \\ \hline
Intern    & X             & X    & X               & X                & X               & X         \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Unit Testing Frameworks}
\end{table}
\FloatBarrier
\footnotesize

* Mocha requires a separate assertion, which leaves the options for assertion styles entirely up to the developer.

\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Free & GitHub & Other Repos & Multi-Language & Online & Beta \\ \hline
Jenkins   & X    & X*     & X*          & X*             & X*     &      \\ \hline
Travis    & X    & X      &             & X              & X      &      \\ \hline
Semaphore &      & X      &             & X              & X      &      \\ \hline
MagnumCI  & X    & X      & X           & X              & X      & X    \\ \hline
Drone.io  & X    & X      & X           & X              & X      &      \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier

@@

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
In this chapter, we will outline our final choices for frameworks and why we chose them.

\section{Chosen Toolset}
After evaluating a number of different combinations and tools, we came to the following setup:
\begin{itemize}
  \item Unit Testing: Mocha with Chai.js
  \item Continuous Integration: MagnumCI
  \item Browser Testing: Nightwatch
  \item Misc:
    \begin{itemize}
      \item Coverage: Istanbul
      \item Task Runner: Grunt
      \item Package Manager: NPM (sort of a given when working with Node.js)
    \end{itemize}
\end{itemize}

@@

After the tests have been written, the developer can run them using the \lstinline{mocha} command. There are a number of command-line arguments available to the mocha command which are well documented and which we won't talk about here. We will talk about the one that we used consistently, that being \lstinline{-R}. The \lstinline{-R} argument allows the developer to specify how the test results will be printed and formatted. Mocha offers seventeen different reporters with more reporters available online and the ability to create custom reporters. We used the \lstinline{spec} reporter because it gave us the information we wanted. All together, our mocha test command was \lstinline{mocha -R spec .}, the final \lstinline{.} being the directory where the tests are located.

@@

\subsection{Setting up Nightwatch}
Installing Nightwatch consists of just installing another npm module. \lstinline{npm install -g nightwatch}. In addition to Nightwatch, the developer needs Selenium. The easiest way is to just download the jar straight from the Google repository here: ``http://selenium-release.storage.googleapis.com/index.html''. Once the developer has the JAR and places it somewhere, Nightwatch is ready to be configured and run. Nightwatch configuration happens in a json file that is pointed to when the developer executes Nightwatch.

@@

For running the browser tests, we recommend using the CI tool. With some setup on the CI of choice, the developer can get Nightwatch running. Most CI setups have either Firefox pre-installed or Xvfb (a windowless X11 process). All that's required is to install Firefox if needed and create an X11 window using Xvfb if needed. In the CI setup, after installing all the prerequisites, the developer should start their application. Next, export the \lstinline{DISPLAY} environment variable, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} to start the ``window'' that will be used. Finally, run Nightwatch, \lstinline{nightwatch -c path_to_nightwatch_config} and enjoy UI testing that doesn't take over the workstation.

@@

\subsection{``A 2-Layer Model for the White-Box Testing of Web Applications'' \cite{2LayerModel}}
A couple of gentlemen at the Center for Scientific Research and Technology in Povo, Italy came with a model for white-box testing of web applications. (White box testing is when the developer is given access to the underlying code.) This paper breaks up the testing process into two abstraction levels, the navigation model, the way in which a webpage goes from page to page, and the control flow model, the way in which information is passed and stored on a given page or between pages. These constitute the 2-layers in the title. The navigation model represents high-level test cases, like asserting that a given link redirects to the correct location, while control flow represents low-level test cases, like making sure data is persisted between pages.

@@

\subsection{``Invariant-Based Automatic Testing of AJAX User Interfaces'' \cite{InvariantBasedUseInterfaces}}
Two individuals from the SOftware Engineering Research Group at Delft University in the Netherlands came up with a way to automatically test AJAX UI. The core of this idea is using a crawler to infer a flow graph. This paper outlines an plugin for an automated tool, ATUSA, for creating state validators and test suites for covering paths discovered during crawling (with a separate tool, CRAWLJAX). Their tests show that with minimal manual effort, the use of ATUSA can lead to high code coverage and error discovery.

@@

\subsection{``JSART: JavaScript Assertion-based Regression Testing'' \cite{JSART}}
Two students from the University of British Columbia created a tool called JSART that uses run-time code instrumentation and analysis to infer invariants that can be used for regression testing. When the code runs, JSART creates a number of test cases that will be run the next time the code executes. The point being to catch any discrepancies between old code and new code. They ran their tool on nine web systems with fairly strong results. The tool was not perfect and occasionally created inappropriate tests, but generally the tests were appropriate and useful.

@@

\subsection{``DOM Transactions for Testing JavaScript'' \cite{DOMTransactions}}
Three people from Albert Ludwigs University in Germany came up with a way to deal with test fixtures that are built and torn down frequently. When testing JavaScript, many of one's tests will change the underlying web page in some way. This is often different from testing traditional software where components are separated. In order to test JavaScript, test fixtures for setting up the page and tearing down the page are exceptionally important. Because these fixtures are being made and torn down frequently, this paper discusses a way to utilize transactional memory to quickly get the web page into the right state without constant setup and tear down.

@@

\subsection{``Testing Web Applications in Practice'' \cite{TestingInPractice}}
Four students from the University of Seville, Spain published a paper with an overview of web testing. This paper was more of an introduction to testing, outlining the concepts of “Unit Testing”, “Integration Testing”, “Regression Testing”, testing the client versus testing the server, and a few others. It also describes how to test an actual web application using PHPUnit, a library similar to JUnit, for those developers familiar with Java. When writing their tests, they suggest taking more abstract actions and breaking them up into their functional parts and testing each of those. As an example, inserting a customer into the database (albeit not that abstract) is broken into tests for the function that inserts the customer and tests for making sure the customer makes it into the database.

@@

\subsection{``Contract-Driven Testing of JavaScript Code'' \cite{ContractDrivenTesting}}
Two individuals from the Albert Ludwigs University in Germany created a tool, JSConTest, that provides a framework for making contracts for a JavaScript program, allowing for guided random testing on inputs and outputs. Contracts in JSConTest are comments above each function that are of the form ``type -> type''. More complicated forms can introduce parenthesis for function types. In general, JSConTest is useful for detecting type errors on input or output based on the operations performed within a function on the input and the result being output.

@@

\subsection{``JAWS: A JavaScript API for the Efficient Testing and Integration of Semantic Web Services'' \cite{JAWS}}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (JavaScript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that one visits personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.

@@

\subsection{``WebMate: A Tool for Testing Web 2.0 Applications'' \cite{WebMate}}
Four people from Saarland University in Germany created a tool, WebMate, for automatically navigating web-pages with dynamic content and data. WebMate's goal is to output a usage model for testing purposes. This usage model allows tests to be focused on navigation as well as functionality. This dual usage leads to the ability to test the experience as well as the functions. In addition, WebMate can be used for Cross-Browser testing by running it on multiple browsers and comparing the results. In essence, WebMate is a web application crawler seeking to automatically suss out the layout and interaction between web pages to provide a model to the tester, be it a developer or the automatic testing capabilities of WebMate.

@@

\subsection{``Continuous Testing with Ruby, Rails, and JavaScript'' \cite{BookContinuousTesting}}
The well known book by Rady and Coffin talks about Continuous Testing and has lots of examples. The last two chapters of the book, six and seven, talk about setting up a Continuous Testing environment for JavaScript using Node.js and a number of other tools. It fit almost perfectly with our project and was used as the basis of our testing setup. They use JSLint for linting, Jasmine for test cases, and Watchr for running the tests continuously. Lastly it discussed writing effective tests, which is always important.

@@

\subsection{``Finding Bugs In Dynamic Web Applications'' \cite{FindingBugs}}
Seven researchers from the MIT Computer Science and Artificial Intelligence Lab wrote a paper addressing testing in dynamic web applications. Common testing techniques were not made to work with dynamic content that can be generated at the drop of a hat or click of a button. Therefore, common testing techniques are inadequate for testing dynamic web applications. This paper discusses ways to find bugs in these new-fangled dynamic web applications. They use a new technique and extended a tool called Apollo. This technique generates dynamic test cases based on concrete and symbolic execution. ``The basic idea is to execute an application on an initial input (e.g., an unconstrained or randomly chosen input), and then on additional inputs obtained by solving constraints derived from exercised control flow paths.''

@@

\subsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications. What they note in particular is that when using web services, the developer rarely has access to the source code and must therefore black-box test them. Corollary to that is that the developer has to implicitly trust whoever made the service. They go through and discuss a number of frameworks and come to the conclusion that it's most certainly not a solved problem for the following reasons: The frequency of testing required, Testing without disrupting the operation of the service, Determining when testing is required and which operations need to be tested. Regarding the frequency of testing, web services often change in effort to make improvements, but those improvements can change the services and break tests. Testing without disrupting service is difficult because these services often limit accesses or simultaneous access of both a test and a running web application. Finally, determining when and what to test comes back to the trust issue. Some services provide their own testing metrics that include code coverage, number of tests, etc, but the developer must trust that the service is thoroughly tested, not just tested enough to provide interesting metrics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%
%%% Sample App 
%%%   Talk about test app
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Testing Frameworks Survey}
In the following chapter we will discuss the testing frameworks that we looked at and the application we used to evaluate them. This chapter will conclude with a set of decision matrices outlining the strengths of each individual framework and where they overlap.

\section{ToDo Application}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our final evaluation application. We chose a ToDo application made with Express.js, Node.js, and MongoDB.\cite{ToDoAppHomePage} Our choice of this application comes from its limited functionality and the ease of understanding the interactions that take place within the application, i.e. adding tasks to a ToDo list, marking tasks as completed, and viewing completed tasks. Here is a brief preview of the application:

@@

In addition to the simplicity and ease of understanding, this application was selected because it included Node.js and MongoDB as we wanted to see if the tools would be able to handle our final evaluation application which also uses those two.

One of the challenges in testing that we quickly came across was the asynchronous nature of the MongoDB function calls. As many web applications feature asynchronous calls, we will be discussing how the following frameworks deal with asynchronous test support.

\subsection{The Average Web Application}
In an effort to create a detailed and in-depth workflow and collection of tools, we have chosen to focus on web applications that use Node.js, JavaScript, and a backing Database. Although this will not cover all web application configurations, we wanted to narrow our scope in order to provide a specific, instead of general, set of guidelines and workflow suggestions.

Node.js is in wide use and because it is written in JavaScript we were able to test our client and server code using the same frameworks. Node.js also offers an incredible package manager, NPM, that allows for a smooth and efficient workflow.

JavaScript is the language of HTML5 and Node.js. It used in over 87\% of all websites\cite{JSUsage} and as such allows us to create a workflow to cover a majority of web applications.

Many websites use databases to store user records, items in stock, and a number of other pieces of information. We wanted to make sure that the testing frameworks could support database functionality as it is often pivotal in running web applications.

@@

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the added complexity of running headless browsers.

Nonetheless, we still looked at two options that we will outline briefly below for other developers' reference. The two options outlined below by no means cover all of the headless browser options, they are simply the two that we saw most often discussed by the other testing tools.

\subsubsection{PhantomJS}
PhantomJS\cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS}
ZombieJS\cite{ZombieJS} is the other headless browser that we saw when searching for browser testing tools. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is an offline Continuous Integration tool, the only offline tool that we found with active developement and support. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run a project in. However, once the server has the necessary applications and libraries, the developer can run builds and tests. Jenkins is 100\% free and can connect with public and private repositories alike.

\subsection{Travis}
Travis\cite{Travis} is an online continuous integration framework with 29 active developers working to improve it and 64 repositories that support it at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore}
Semaphore\cite{Semaphore} is an online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI}
MagnumCI\cite{MagnumCI} is another online CI framework. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects.

@@

\subsection{CI By Hand}
Most of what these CI frameworks accomplish can be done by hand.
\todo{Finish this section}

% Strengths
- Similar to Jenkins

% Weaknesses
- Setup by hand
- Uses your machine

@@

Of particular interest is that last feature, \lstinline{watch}. We use grunt's \lstinline{watch} capability to run tests constantly. This feature gives immediate feedback to the developer when they change existing code or write new code after having written a test for it. As long as all the tests are passing, the developer has a good idea that the changes made are regression-tested as well as freshly tested and are ready for publishing or integration.

\subsection{Node Inspector}
Node Inspector\cite{NodeInspector} is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.

@@

\section{Framework Decision Matrices}
In an effort to further expedite the selection of tools, the following decision matrices can be quickly referenced by new developers to decide on which tools are right for them.

\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Assertion Styles  & Test Interfaces & Reporters & AMD & Active Development*   \\ \hline
Jasmine   &                   &                 &           &     & X                     \\ \hline
Mocha     & X**               & X               & X         &     & X                     \\ \hline
Qunit     &                   &                 &           &     & X                     \\ \hline
Intern    & X                 & X               & X         & X   & X                     \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Unit Testing Frameworks}
\end{table}
\FloatBarrier
\footnotesize

* Active Development is defined as any commit within the last month.

** Mocha requires a separate assertion, which leaves the options for assertion styles entirely up to the developer.

\normalsize
\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & GitHub & Other Repos & Multi-Language & Active Development** & GUI Configuration \\ \hline
Jenkins   & X*     & X*          & X*             & X*                  & X                 \\ \hline
Travis    & X      &             & X              &                     &                   \\ \hline
Semaphore & X      &             & X              & X                   & X                 \\ \hline
MagnumCI  & X      & X           & X              & X                   & X                 \\ \hline
Drone.io  & X      & X           & X              & X                   & X                 \\ \hline
Manual    &        & X           & X              & X                   &                   \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier
\footnotesize

@@

** Active Development is defined as any commit within the last month.

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Framework Selection}
In this chapter, we will outline our final choices for frameworks and why we chose them.

\section{Chosen Tools}
After evaluating a number of different combinations and tools, we came to the following setup:
\begin{itemize}
  \item Unit Testing: Mocha with Chai.js
  \item Continuous Integration: MagnumCI
  \item Browser Testing: Nightwatch
  \item Misc:
    \begin{itemize}
      \item Coverage: Istanbul
      \item Task Runner: Grunt
      \item Package Manager: NPM (sort of a given when working with Node.js)
    \end{itemize}
\end{itemize}

@@

The tests can be put in any folder, but something to keep in mind is that the tests will reference the source code. The further away from the source code the tests are, the longer the paths to the source code in the test files.

For reference here's what a simple test file might look like:
\begin{lstlisting}
// repo/src/tests/myTestFile.js

var assert = require('chai').assert;

describe("My Test Suite", function () {
  var myModule = require('../my_module.js');

  it("should run my function", function () {
    var result = myModule.myFunction();
    var expected_result = 10;

    assert.equal(result, expected_result);
  });
});
\end{lstlisting}

After the tests have been written, the developer can run them using the \lstinline{mocha} command. There are a number of command-line arguments available to the mocha command which are well documented and which we won't talk about here. We will talk about the one that we used consistently, that being \lstinline{-R}. The \lstinline{-R} argument allows the developer to specify how the test results will be printed and formatted. Mocha offers seventeen different reporters with more reporters available online and the ability to create custom reporters. We chose the \lstinline{spec} reporter because it outlined each individual suite and test case. Other reporters generally provide less information such as the \lstinline{progress} reporter which just shows a progress bar. All together, our mocha test command was \lstinline{mocha -R spec .}, the final \lstinline{.} being the directory where the tests are located.

@@

\subsection{Setting up Nightwatch}
Installing Nightwatch consists of just installing another npm module. \lstinline{npm install -g nightwatch}. In addition to Nightwatch, the developer needs Selenium. The easiest way is to just download the ``selenium-server-standalone'' jar straight from the Google repository here: ``http://selenium-release.storage.googleapis.com/index.html''. Our tests ran using ``selenium-server-standalone-2.40.0'' but any version 2.40+ should work. Once the developer has the JAR and places it in a location they will remember, generally along with other similar executables in a bin or library directory, Nightwatch is ready to be configured and run. Nightwatch configuration happens in a json file that is pointed to when the developer executes Nightwatch.

@@

For running the browser tests, we recommend using the CI tool. Most CI setups have Xvfb (a windowless X11 process) and some even have Firefox pre-installed. Nightwatch requires both to be installed. If Firefox needs to be installed, the developer can use the CI framework's package manager to install it. For example, if the package manager is \lstinline{apt-get}: ``\lstinline{apt-get install firefox}''. In the CI setup, after installing all the prerequisites, the developer should start their application. Next, export the \lstinline{DISPLAY} environment variable, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} to start the ``window'' that will be used. Finally, run Nightwatch, \lstinline{nightwatch -c path_to_nightwatch_config} and enjoy UI testing that doesn't take over the workstation.

@@

\subsection{``A 2-Layer Model for the White-Box Testing of Web Applications''}
A couple of gentlemen at the Center for Scientific Research and Technology in Povo, Italy came up with a model for white-box testing of web applications\cite{2LayerModel}. (White box testing is when the developer is given access to the underlying code.) This paper breaks up the testing process into two abstraction levels, the navigation model, the way in which a webpage goes from page to page, and the control flow model, the way in which information is passed and stored on a given page or between pages. These constitute the 2-layers in the title. The navigation model represents high-level test cases, like asserting that a given link redirects to the correct location, while control flow represents low-level test cases, like making sure data is persisted between pages.

@@

\subsection{``Invariant-Based Automatic Testing of AJAX User Interfaces''}
Two individuals from the Software Engineering Research Group at Delft University in the Netherlands came up with a way to automatically test AJAX UI\cite{InvariantBasedUseInterfaces}. The core of this idea is using a crawler to infer a flow graph. This paper outlines an plugin for an automated tool, ATUSA, for creating state validators and test suites for covering paths discovered during crawling (with a separate tool, CRAWLJAX). Their tests show that with minimal manual effort, the use of ATUSA can lead to high code coverage and error discovery.

@@

\subsection{``JSART: JavaScript Assertion-based Regression Testing''}
Two students from the University of British Columbia created a tool called JSART that uses run-time code instrumentation and analysis to infer invariants that can be used for regression testing\cite{JSART}. When the code runs, JSART creates a number of test cases that will be run the next time the code executes. The point being to catch any discrepancies between old code and new code. They ran their tool on nine web systems with fairly strong results. The tool was not perfect and occasionally created inappropriate tests, but generally the tests were appropriate and useful.

@@

\subsection{``DOM Transactions for Testing JavaScript''}
Three people from Albert Ludwigs University in Germany came up with a way to deal with test fixtures that are built and torn down frequently\cite{DOMTransactions}. When testing JavaScript, many of one's tests will change the underlying web page in some way. This is often different from testing traditional software where components are separated. In order to test JavaScript, test fixtures for setting up the page and tearing down the page are exceptionally important. Because these fixtures are being made and torn down frequently, this paper discusses a way to utilize transactional memory to quickly get the web page into the right state without constant setup and tear down.

@@

\subsection{``Testing Web Applications in Practice''}
Four students from the University of Seville, Spain published a paper with an overview of web testing\cite{TestingInPractice}. This paper was more of an introduction to testing, outlining the concepts of “Unit Testing”, “Integration Testing”, “Regression Testing”, testing the client versus testing the server, and a few others. It also describes how to test an actual web application using PHPUnit, a library similar to JUnit, for those developers familiar with Java. When writing their tests, they suggest taking more abstract actions and breaking them up into their functional parts and testing each of those. As an example, inserting a customer into the database (albeit not that abstract) is broken into tests for the function that inserts the customer and tests for making sure the customer makes it into the database.

@@

\subsection{``Contract-Driven Testing of JavaScript Code''}
Two individuals from the Albert Ludwigs University in Germany created a tool, JSConTest, that provides a framework for making contracts for a JavaScript program, allowing for guided random testing on inputs and outputs\cite{ContractDrivenTesting}. Contracts in JSConTest are comments above each function that are of the form ``type -> type''. More complicated forms can introduce parenthesis for function types. In general, JSConTest is useful for detecting type errors on input or output based on the operations performed within a function on the input and the result being output.

@@

\subsection{``JAWS: A JavaScript API for the Efficient Testing and Integration of Semantic Web Services''}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (JavaScript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services\cite{JAWS}. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that one visits personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.

@@

\subsection{``WebMate: A Tool for Testing Web 2.0 Applications''}
Four people from Saarland University in Germany created a tool, WebMate, for automatically navigating web-pages with dynamic content and data\cite{WebMate}. WebMate's goal is to output a usage model for testing purposes. This usage model allows tests to be focused on navigation as well as functionality. This dual usage leads to the ability to test the experience as well as the functions. In addition, WebMate can be used for Cross-Browser testing by running it on multiple browsers and comparing the results. In essence, WebMate is a web application crawler seeking to automatically suss out the layout and interaction between web pages to provide a model to the tester, be it a developer or the automatic testing capabilities of WebMate.

@@

\subsection{``Continuous Testing with Ruby, Rails, and JavaScript''}
This well known book by Rady and Coffin\cite{BookContinuousTesting} talks about Continuous Testing and has lots of examples. The last two chapters of the book, six and seven, talk about setting up a Continuous Testing environment for JavaScript using Node.js and a number of other tools. It fit almost perfectly with our project and was used as the basis of our testing setup. They use JSLint for linting, Jasmine for test cases, and Watchr for running the tests continuously. Lastly it discussed writing effective tests, which is always important.

@@

\subsection{``Finding Bugs In Dynamic Web Applications''}
Seven researchers from the MIT Computer Science and Artificial Intelligence Lab wrote a paper addressing testing in dynamic web applications\cite{FindingBugs}. Common testing techniques were not made to work with dynamic content that can be generated at the drop of a hat or click of a button. Therefore, common testing techniques are inadequate for testing dynamic web applications. This paper discusses ways to find bugs in these new-fangled dynamic web applications. They use a new technique and extended a tool called Apollo. This technique generates dynamic test cases based on concrete and symbolic execution. ``The basic idea is to execute an application on an initial input (e.g., an unconstrained or randomly chosen input), and then on additional inputs obtained by solving constraints derived from exercised control flow paths.''

@@

\subsection{``Testing Web Services: A Survey''}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services\cite{TestingWebServicesSurvey}. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications. What they note in particular is that when using web services, the developer rarely has access to the source code and must therefore black-box test them. Corollary to that is that the developer has to implicitly trust whoever made the service. They go through and discuss a number of frameworks and come to the conclusion that it's most certainly not a solved problem for the following reasons: The frequency of testing required, Testing without disrupting the operation of the service, Determining when testing is required and which operations need to be tested. Regarding the frequency of testing, web services often change in effort to make improvements, but those improvements can change the services and break tests. Testing without disrupting service is difficult because these services often limit accesses or simultaneous access of both a test and a running web application. Finally, determining when and what to test comes back to the trust issue. Some services provide their own testing metrics that include code coverage, number of tests, etc, but the developer must trust that the service is thoroughly tested, not just tested enough to provide interesting metrics.

\subsection{``A Framework for Testing RESTful Web Services''}
Two people from the University of Dakota School of Aerospace Studies outline a framework for testing RESTful web services\cite{RESTfulFramework}. RESTful web services, short for Representation State Transfer, are, in the context of web applications, a name for web APIs that conform to a set of constraints. In particular they must offer four request methods: GET, POST, PUT, and DELETE. These methods generally connect to a database or other storage system in order to store, retrieve, or delete entries therein.
